Chord: A Static and Dynamic Program Analysis Framework for Java

### 2010-09-06 main/doc/chord_sysprops.tex
minor
added new property chord.analysis.exclude to exclude specified tasks; also improved error messages regarding ambiguous tasks in both classic and modern projects

@@

\item
\code{chord.dynamic.timeout} \\
{\bf Type:} int \\
{\bf Description:} The amount of time, in milliseconds, after which to kill the process running the given program during dynamic analysis, or -1 if the process must never be killed. \\
{\bf Default value:} -1

\item
\code{chord.dynamic.silent} \\
{\bf Type:} bool \\
{\bf Description:} Whether or not to emit warnings while running the given program during dynamic analysis. \\
{\bf Default value:} false
\end{itemize}

>>>>

\item
\code{chord.analysis.exclude} \\
{\bf Type:} string list \\
{\bf Descrption:} Names of program analyses written in Java or Datalog to be excluded from the project. \\
{\bf Default value:} {\tt ""}

@@

\item
\code{chord.dynamic.timeout} \\
{\bf Type:} int \\
{\bf Description:} The amount of time, in milliseconds, after which to kill the process running the given program during dynamic analysis, or -1 if the process must never be killed. \\
{\bf Default value:} -1
\end{itemize}
